Fit by design: Developing seed–substrate combinations to adapt dike grasslands to microclimatic variation

### 2023-08-09 manuscript.Rmd
Update manuscript.Rmd

```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_3_600dpi_16.5x5cm.tiff")
  )
```

>>>>

```{r fig.id = "effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_3_300dpi_16.5x5cm.tiff")
  )
```
